Norwegian citizen science data exploration

### 2018-02-15 paper.Rmd
Add map comparing observations to linear model generated

gridsizeinkm <- 50
cellsize <- (lat_dataset[2] - lat_dataset[1]) * gridsizeinkm * .0016

@@

The number of `r summarize_list(obs_filter[-1])` in Norway per `r gridsizeinkm` x `r gridsizeinkm` km cs cells, versus the human population in those cells. R² of the linaer regression is `r summary(lm(num ~ TOT_P, data=num_vs_pop))$r.squared`. R² of the log linaer regression is `r summary(lm(log10(num) ~ log10(TOT_P), data=num_vs_pop))$r.squared`.

@@

>>>>

gridsizeinkm <- 30
cellsize <- (lat_dataset[2] - lat_dataset[1]) * gridsizeinkm * .0018

@@

The number of `r summarize_list(obs_filter[-1])` in Norway per `r gridsizeinkm` x `r gridsizeinkm` km cs cells, versus the human population in those cells. R² of the linaer regression is `r summary(lm(num ~ TOT_P, data=num_vs_pop))$r.squared`.

@@

```{r relative_to_lm_plot_rasterized, messages=FALSE, echo=FALSE}

B0 <- (summary(lm(num ~ TOT_P, data=num_vs_pop))$coefficients)["(Intercept)","Estimate"]
B1 <- (summary(lm(num ~ TOT_P, data=num_vs_pop))$coefficients)["TOT_P","Estimate"]

num_vs_pop$relativeToLM <- num_vs_pop$num / (B0 + B1 * num_vs_pop$TOT_P)

ggplot(num_vs_pop) + 
    annotation_map(world_map, fill="gray50", colour="gray50") +
    geom_point(aes(x=long_rounded, y=lat_rounded, color=log(relativeToLM)), shape=15, size=cellsize) +
    scale_color_distiller(palette = "Spectral") +
    annotation_map(world_map, fill=NA, colour="gray30") +
    theme(panel.background = element_rect(fill="aliceblue"), legend.position = "right") +
    coord_map(projection = "gnomonic", orientation=c(60, 16, -5),
              xlim=long_dataset,  # limits on longitude
              ylim=lat_dataset) + # limits on latitude
   xlab("Longitude") + ylab("Latitude")

The log number of `r summarize_list(obs_filter[-1])` observations in Norway divided by the number predicted by the regression line (numberOfObservations = `r B0` + `r B1` * humanPopulation),  within `r gridsizeinkm` x `r gridsizeinkm` km cells.
